Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-15 RR_manuscript/Draft_RR.tex
:memo: - edit second model with details about deviation from posterior

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=4cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{cleveref}
\setlength{\marginparwidth}{2cm}
\usepackage[todonotes={textsize=tiny}]{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g. Jongman, Wayland, and Wong 2000; Lisker 1986; \textbf{summerfield1984?}; Winter 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).

@@

As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic point estimate by the individual standardized effect sizes relate to those same predictors.
We will fit two Bayesian regression models, one for (a) and one for (b).
with each team's group-level coefficient \(\alpha_{\text{t}[i]}\) as the outcome variable, and the analytical and demographic factors described below as predictors.
The coefficient \(\alpha_{\text{t}[i]}\) can be interpreted as the deviation score of the team's \(\eta_i\) from the meta-analytic point estimate, allowing us to determine potential effects of analytical and demographic factors on how the teams deviate from the meta-analytic mean.
Since each \(\alpha_{\text{t}[i]}\) comes with uncertainty, quantified by its standard deviation \(\sigma_{\alpha_{\text{t}[i]}}\), we will fit a measurement-error model, as we did in the meta-analytic model above.

@@

\hypertarget{ana-archive}{%
\subsubsection{Data managment}\label{ana-archive}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-arts2011overspecification}{}%
Arts, Anja, Alfons Maes, Leo GM Noordman, and Carel Jansen. 2011. {``Overspecification in Written Instruction.''} \emph{Linguistics} 49 (3): 555--74.

\leavevmode\hypertarget{ref-baselga2020}{}%
Baselga, Andres, David Orme, Sebastien Villeger, Julien De Bortoli, Fabien Leprieur, and Maxime Logez. 2020. {``{b}etapart: Partitioning Beta Diversity into Turnover and Nestedness Components.''} \url{https://CRAN.R-project.org/package=betapart}.

\leavevmode\hypertarget{ref-bastiaansen2020}{}%
Bastiaansen, Jojanneke A., Yoram K. Kunkels, Frank J. Blaauw, Steven M. Boker, Eva Ceulemans, Meng Chen, Sy-Miin Chow, et al. 2020. {``Time to Get Personal? The Impact of Researchers Choices on the Selection of Treatment Targets Using the Experience Sampling Methodology.''} \emph{Journal of Psychosomatic Research} 137: 110211.

\leavevmode\hypertarget{ref-botvinik-nezer2020}{}%
Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F. Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al. 2020a. {``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature} 582 (7810): 84--88.

\leavevmode\hypertarget{ref-botvinik2020variability}{}%
Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al. 2020b. {``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature}, 1--7.

\leavevmode\hypertarget{ref-box1976science}{}%
Box, George EP. 1976. {``Science and Statistics.''} \emph{Journal of the American Statistical Association} 71 (356): 791--99.

\leavevmode\hypertarget{ref-brugger2001}{}%
Brugger, Peter. 2001. {``From Haunted Brain to Haunted Science: A Cognitive Neuroscience View of Paranormal and Pseudoscientific Thought.''} \emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, January, 195--213.

\leavevmode\hypertarget{ref-burkner2017}{}%
Bürkner, Paul-Christian. 2017. {``{brms}: An {R} Package for {Bayesian} Multilevel Models Using {Stan}.''} \emph{Journal of Statistical Software} 80 (1): 1--28. \url{https://doi.org/10.18637/jss.v080.i01}.

\leavevmode\hypertarget{ref-camerer2018evaluating}{}%
Camerer, Colin F, Anna Dreber, Felix Holzmeister, Teck-Hua Ho, Jürgen Huber, Magnus Johannesson, Michael Kirchler, et al. 2018. {``Evaluating the Replicability of Social Science Experiments in Nature and Science Between 2010 and 2015.''} \emph{Nature Human Behaviour} 2 (9): 637--44. \url{https://doi.org/10.1038/s41562-018-0399-z}.

\leavevmode\hypertarget{ref-open2015estimating}{}%
Collaboration, Open Science. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.

\leavevmode\hypertarget{ref-de2014thought}{}%
De Groot, Adriaan D. 2014. \emph{Thought and Choice in Chess}. Vol. 4. Walter de Gruyter GmbH \& Co KG.

\leavevmode\hypertarget{ref-degen2020redundancy}{}%
Degen, Judith, Robert D Hawkins, Caroline Graf, Elisa Kreiss, and Noah D Goodman. 2020. {``When Redundancy Is Useful: A Bayesian Approach to {`Overinformative'} Referring Expressions.''} \emph{Psychological Review}.

\leavevmode\hypertarget{ref-dice1945}{}%
Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.

\leavevmode\hypertarget{ref-dutilh2019}{}%
Dutilh, Gilles, Jeffrey Annis, Scott D. Brown, Peter Cassey, Nathan J. Evans, Raoul Grasman, Guy E. Hawkins, et al. 2019. {``The Quality of Response Time Data Inference: A Blinded, Collaborative Assessment of the Validity of Cognitive Models.''} \emph{Psychonomic Bulletin \& Review} 26 (4): 1051--69.

\leavevmode\hypertarget{ref-egger1997}{}%
Egger, Matthias, George Davey Smith, Martin Schneider, and Christoph Minder. 1997. {``Bias in Meta-Analysis Detected by a Simple, Graphical Test.''} \emph{British Medical Journal} 315: 629--34.

\leavevmode\hypertarget{ref-fischhoff1975hindsight}{}%
Fischhoff, Baruch. 1975. {``Hindsight Is Not Equal to Foresight: The Effect of Outcome Knowledge on Judgment Under Uncertainty.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 1 (3): 288.

\leavevmode\hypertarget{ref-flake2020}{}%
Flake, Jessica Kay, and Eiko I. Fried. 2020. {``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (4): 456--65. \url{https://doi.org/10.1177/2515245920952393}.

\leavevmode\hypertarget{ref-foulkes2006}{}%
Foulkes, Paul, and Gerard Docherty. 2006. {``The Social Life of Phonetics and Phonology.''} \emph{Journal of Phonetics} 34 (4): 409--38.

\leavevmode\hypertarget{ref-gatt2013we}{}%
Gatt, Albert, Roger PG van Gompel, Kees van Deemter, and Emiel Krahmer. 2013. {``Are We Bayesian Referring Expression Generators.''} In. Cognitive Science Society.

\leavevmode\hypertarget{ref-gelman2014statistical}{}%
Gelman, Andrew, and Eric Loken. 2014. {``The Statistical Crisis in Science: Data-Dependent Analysis--a" Garden of Forking Paths"--Explains Why Many Statistically Significant Comparisons Don't Hold Up.''} \emph{American Scientist} 102 (6): 460--66.

\leavevmode\hypertarget{ref-gordon2017acoustic}{}%
Gordon, Matthew, and Timo Roettger. 2017. {``Acoustic Correlates of Word Stress: A Cross-Linguistic Survey.''} \emph{Linguistics Vanguard} 3 (1): 1--11.

\leavevmode\hypertarget{ref-grice1975logic}{}%
Grice, Herbert P. 1975. {``Logic and Conversation.''} In \emph{Speech Acts}, 41--58. Brill.

\leavevmode\hypertarget{ref-hawkins2004influence}{}%
Hawkins, Sarah, and Noël Nguyen. 2004. {``Influence of Syllable-Coda Voicing on the Acoustic Properties of Syllable-Onset /l/ in {E}nglish.''} \emph{Journal of Phonetics} 32 (2): 199--231.

\leavevmode\hypertarget{ref-jongman2000acoustic}{}%
Jongman, Allard, Ratree Wayland, and Serena Wong. 2000. {``Acoustic Characteristics of English Fricatives.''} \emph{The Journal of the Acoustical Society of America} 108 (3): 1252--63.

\leavevmode\hypertarget{ref-klein2018practical}{}%
Klein, Olivier, Tom E Hardwicke, Frederik Aust, Johannes Breuer, Henrik Danielsson, Alicia Hofelich Mohr, Hans IJzerman, et al. 2018. {``A Practical Guide for Transparency in Psychological Science.''} \emph{Collabra: Psychology} 4 (1).

\leavevmode\hypertarget{ref-knight2000}{}%
Knight, K. 2000. \emph{Mathematical Statistics}. Chapman; Hall, New York.

\leavevmode\hypertarget{ref-koole2012rewarding}{}%
Koole, Sander L, and Daniël Lakens. 2012. {``Rewarding Replications: A Sure and Simple Way to Improve Psychological Science.''} \emph{Perspectives on Psychological Science} 7 (6): 608--14.

\leavevmode\hypertarget{ref-ladd2008intonational}{}%
Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.

\leavevmode\hypertarget{ref-lau2006}{}%
Lau, Joseph, John P. A. Ioannidis, Norma Terrin, Christopher H. Schmid, and Ingram Olkin. 2006. {``The Case of the Misleading Funnel Plot.''} \emph{British Medical Journal} 333 (7568): 597--600.

\leavevmode\hypertarget{ref-light1984}{}%
Light, Richard J., and David B. Pillemer. 1984. \emph{Summing up; the Science of Reviewing Research}. Cambridge, MA (USA) Harvard Univ. Press.

\leavevmode\hypertarget{ref-lisker1977rapid}{}%
Lisker, Leigh. 1977. {``Rapid Versus Rabid: A Catalogue of Acoustic Features That May Cue the Distinction.''} \emph{The Journal of the Acoustical Society of America} 62 (S1): S77--78.

\leavevmode\hypertarget{ref-lisker1986voicing}{}%
---------. 1986. {``{`Voicing'} in {E}nglish: A Catalogue of Acoustic Features Signaling /b/ Versus /p/ in Trochees.''} \emph{Language and Speech} 29 (1): 3--11.

\leavevmode\hypertarget{ref-miguel2014promoting}{}%
Miguel, Edward, Colin Camerer, Katherine Casey, Joshua Cohen, Kevin M Esterling, Alan Gerber, Rachel Glennerster, et al. 2014. {``Promoting Transparency in Social Science Research.''} \emph{Science} 343 (6166): 30--31.

\leavevmode\hypertarget{ref-nickerson1998confirmation}{}%
Nickerson, Raymond S. 1998. {``Confirmation Bias: A Ubiquitous Phenomenon in Many Guises.''} \emph{Review of General Psychology} 2 (2): 175--220.

\leavevmode\hypertarget{ref-nosek2014method}{}%
Nosek, Brian A, and Daniël Lakens. 2014. {``A Method to Increase the Credibility of Published Results.''} \emph{Social Psychology} 45 (3): 137--41.

\leavevmode\hypertarget{ref-ogden2004}{}%
Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.

\leavevmode\hypertarget{ref-paraboni2007generating}{}%
Paraboni, Ivandré, Kees Van Deemter, and Judith Masthoff. 2007. {``Generating Referring Expressions: Making Referents Easy to Identify.''} \emph{Computational Linguistics} 33 (2): 229--54.

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. 2020. \emph{R: A Language and Environment for Statistical Computing}. Vienna, Austria: R Foundation for Statistical Computing. \url{https://www.R-project.org/}.

\leavevmode\hypertarget{ref-roettger2019researcher}{}%
Roettger, Timo B. 2019. {``Researcher Degrees of Freedom in Phonetic Research.''} \emph{Laboratory Phonology: Journal of the Association for Laboratory Phonology} 10 (1).

\leavevmode\hypertarget{ref-rotello2015more}{}%
Rotello, Caren M, Evan Heit, and Chad Dubé. 2015. {``When More Data Steer Us Wrong: {R}eplications with the Wrong Dependent Measure Perpetuate Erroneous Conclusions.''} \emph{Psychonomic Bulletin \& Review} 22 (4): 944--54.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.},
  pdfkeywords={crowdsourcing science, data analysis, scientific transparency, speech, acoustic analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=4cm]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{cleveref}
\setlength{\marginparwidth}{2cm}
\usepackage[todonotes={textsize=tiny}]{changes}
\definechangesauthor[name={Stefano Coretta}, color=red]{SC}
\definechangesauthor[name={Timo Röttger}, color=blue]{TR}
\definechangesauthor[name={Joseph Casillas}, color=orange]{JC}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Speech categories are inherently multidimensional and dynamic: they consist of clusters of parameters that are modulated over time.
The acoustic parameters of one category are usually asynchronous, i.e.~they appear at different time points in the unfolding signal, and overlap with parameters of other categories (e.g. Jongman, Wayland, and Wong 2000; Lisker 1986; Summerfield 1981; Winter 2014).
A classical example is the distinction between voiced and voiceless stops in English (i.e.~/b/ and /p/ in \emph{bear} vs \emph{pear}).
This lexical contrast is manifested by many acoustic features which can differ depending on several factors, such as position of the consonant in the word and surrounding sounds (Lisker 1977).
Furthermore, correlates of the contrast can even be found away from the consonant, in temporally distant speech units.
For example, the initial /l/ of the English words \emph{led} and \emph{let} is affected by the voicing of the final consonant (/t, d/) (Hawkins and Nguyen 2004).

@@

As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
We will fit two Bayesian regression models, one for (a) and one for (b).

@@

\textbf{Models specification}. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance \(Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})\).

\hypertarget{ana-archive}{%
\subsubsection{Data management}\label{ana-archive}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-arts2011overspecification}{}}%
Arts, Anja, Alfons Maes, Leo GM Noordman, and Carel Jansen. 2011. {``Overspecification in Written Instruction.''} \emph{Linguistics} 49 (3): 555--74.

\leavevmode\vadjust pre{\hypertarget{ref-baselga2020}{}}%
Baselga, Andres, David Orme, Sebastien Villeger, Julien De Bortoli, Fabien Leprieur, and Maxime Logez. 2020. {``{b}etapart: Partitioning Beta Diversity into Turnover and Nestedness Components.''} \url{https://CRAN.R-project.org/package=betapart}.

\leavevmode\vadjust pre{\hypertarget{ref-bastiaansen2020}{}}%
Bastiaansen, Jojanneke A., Yoram K. Kunkels, Frank J. Blaauw, Steven M. Boker, Eva Ceulemans, Meng Chen, Sy-Miin Chow, et al. 2020. {``Time to Get Personal? The Impact of Researchers Choices on the Selection of Treatment Targets Using the Experience Sampling Methodology.''} \emph{Journal of Psychosomatic Research} 137: 110211.

\leavevmode\vadjust pre{\hypertarget{ref-botvinik-nezer2020}{}}%
Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F. Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al. 2020a. {``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature} 582 (7810): 84--88.

\leavevmode\vadjust pre{\hypertarget{ref-botvinik2020variability}{}}%
Botvinik-Nezer, Rotem, Felix Holzmeister, Colin F Camerer, Anna Dreber, Juergen Huber, Magnus Johannesson, Michael Kirchler, et al. 2020b. {``Variability in the Analysis of a Single Neuroimaging Dataset by Many Teams.''} \emph{Nature}, 1--7.

\leavevmode\vadjust pre{\hypertarget{ref-box1976science}{}}%
Box, George EP. 1976. {``Science and Statistics.''} \emph{Journal of the American Statistical Association} 71 (356): 791--99.

\leavevmode\vadjust pre{\hypertarget{ref-brugger2001}{}}%
Brugger, Peter. 2001. {``From Haunted Brain to Haunted Science: A Cognitive Neuroscience View of Paranormal and Pseudoscientific Thought.''} \emph{Hauntings and Poltergeists: Multidisciplinary Perspectives}, January, 195--213.

\leavevmode\vadjust pre{\hypertarget{ref-burkner2017}{}}%
Bürkner, Paul-Christian. 2017. {``{brms}: An {R} Package for {Bayesian} Multilevel Models Using {Stan}.''} \emph{Journal of Statistical Software} 80 (1): 1--28. \url{https://doi.org/10.18637/jss.v080.i01}.

\leavevmode\vadjust pre{\hypertarget{ref-camerer2018evaluating}{}}%
Camerer, Colin F, Anna Dreber, Felix Holzmeister, Teck-Hua Ho, Jürgen Huber, Magnus Johannesson, Michael Kirchler, et al. 2018. {``Evaluating the Replicability of Social Science Experiments in Nature and Science Between 2010 and 2015.''} \emph{Nature Human Behaviour} 2 (9): 637--44. \url{https://doi.org/10.1038/s41562-018-0399-z}.

\leavevmode\vadjust pre{\hypertarget{ref-open2015estimating}{}}%
Collaboration, Open Science. 2015. {``Estimating the Reproducibility of Psychological Science.''} \emph{Science} 349 (6251). \url{https://doi.org/10.1126/science.aac4716}.

\leavevmode\vadjust pre{\hypertarget{ref-de2014thought}{}}%
De Groot, Adriaan D. 2014. \emph{Thought and Choice in Chess}. Vol. 4. Walter de Gruyter GmbH \& Co KG.

\leavevmode\vadjust pre{\hypertarget{ref-degen2020redundancy}{}}%
Degen, Judith, Robert D Hawkins, Caroline Graf, Elisa Kreiss, and Noah D Goodman. 2020. {``When Redundancy Is Useful: A Bayesian Approach to {`Overinformative'} Referring Expressions.''} \emph{Psychological Review}.

\leavevmode\vadjust pre{\hypertarget{ref-dice1945}{}}%
Dice, Lee Raymond. 1945. {``Measures of the Amount of Ecologic Association Between Species.''} \emph{Ecology} 26 (3): 297--302.

\leavevmode\vadjust pre{\hypertarget{ref-dutilh2019}{}}%
Dutilh, Gilles, Jeffrey Annis, Scott D. Brown, Peter Cassey, Nathan J. Evans, Raoul Grasman, Guy E. Hawkins, et al. 2019. {``The Quality of Response Time Data Inference: A Blinded, Collaborative Assessment of the Validity of Cognitive Models.''} \emph{Psychonomic Bulletin \& Review} 26 (4): 1051--69.

\leavevmode\vadjust pre{\hypertarget{ref-egger1997}{}}%
Egger, Matthias, George Davey Smith, Martin Schneider, and Christoph Minder. 1997. {``Bias in Meta-Analysis Detected by a Simple, Graphical Test.''} \emph{British Medical Journal} 315: 629--34.

\leavevmode\vadjust pre{\hypertarget{ref-fischhoff1975hindsight}{}}%
Fischhoff, Baruch. 1975. {``Hindsight Is Not Equal to Foresight: The Effect of Outcome Knowledge on Judgment Under Uncertainty.''} \emph{Journal of Experimental Psychology: Human Perception and Performance} 1 (3): 288.

\leavevmode\vadjust pre{\hypertarget{ref-flake2020}{}}%
Flake, Jessica Kay, and Eiko I. Fried. 2020. {``Measurement Schmeasurement: Questionable Measurement Practices and How to Avoid Them.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (4): 456--65. \url{https://doi.org/10.1177/2515245920952393}.

\leavevmode\vadjust pre{\hypertarget{ref-foulkes2006}{}}%
Foulkes, Paul, and Gerard Docherty. 2006. {``The Social Life of Phonetics and Phonology.''} \emph{Journal of Phonetics} 34 (4): 409--38.

\leavevmode\vadjust pre{\hypertarget{ref-gatt2013we}{}}%
Gatt, Albert, Roger PG van Gompel, Kees van Deemter, and Emiel Krahmer. 2013. {``Are We Bayesian Referring Expression Generators.''} In. Cognitive Science Society.

\leavevmode\vadjust pre{\hypertarget{ref-gelman2014statistical}{}}%
Gelman, Andrew, and Eric Loken. 2014. {``The Statistical Crisis in Science: Data-Dependent Analysis--a" Garden of Forking Paths"--Explains Why Many Statistically Significant Comparisons Don't Hold Up.''} \emph{American Scientist} 102 (6): 460--66.

\leavevmode\vadjust pre{\hypertarget{ref-gordon2017acoustic}{}}%
Gordon, Matthew, and Timo Roettger. 2017. {``Acoustic Correlates of Word Stress: A Cross-Linguistic Survey.''} \emph{Linguistics Vanguard} 3 (1): 1--11.

\leavevmode\vadjust pre{\hypertarget{ref-grice1975logic}{}}%
Grice, Herbert P. 1975. {``Logic and Conversation.''} In \emph{Speech Acts}, 41--58. Brill.

\leavevmode\vadjust pre{\hypertarget{ref-hawkins2004influence}{}}%
Hawkins, Sarah, and Noël Nguyen. 2004. {``Influence of Syllable-Coda Voicing on the Acoustic Properties of Syllable-Onset /l/ in {E}nglish.''} \emph{Journal of Phonetics} 32 (2): 199--231.

\leavevmode\vadjust pre{\hypertarget{ref-jongman2000acoustic}{}}%
Jongman, Allard, Ratree Wayland, and Serena Wong. 2000. {``Acoustic Characteristics of English Fricatives.''} \emph{The Journal of the Acoustical Society of America} 108 (3): 1252--63.

\leavevmode\vadjust pre{\hypertarget{ref-klein2018practical}{}}%
Klein, Olivier, Tom E Hardwicke, Frederik Aust, Johannes Breuer, Henrik Danielsson, Alicia Hofelich Mohr, Hans IJzerman, et al. 2018. {``A Practical Guide for Transparency in Psychological Science.''} \emph{Collabra: Psychology} 4 (1).

\leavevmode\vadjust pre{\hypertarget{ref-knight2000}{}}%
Knight, K. 2000. \emph{Mathematical Statistics}. Chapman; Hall, New York.

\leavevmode\vadjust pre{\hypertarget{ref-koole2012rewarding}{}}%
Koole, Sander L, and Daniël Lakens. 2012. {``Rewarding Replications: A Sure and Simple Way to Improve Psychological Science.''} \emph{Perspectives on Psychological Science} 7 (6): 608--14.

\leavevmode\vadjust pre{\hypertarget{ref-ladd2008intonational}{}}%
Ladd, D Robert. 2008. \emph{Intonational Phonology}. Cambridge University Press.

\leavevmode\vadjust pre{\hypertarget{ref-lau2006}{}}%
Lau, Joseph, John P. A. Ioannidis, Norma Terrin, Christopher H. Schmid, and Ingram Olkin. 2006. {``The Case of the Misleading Funnel Plot.''} \emph{British Medical Journal} 333 (7568): 597--600.

\leavevmode\vadjust pre{\hypertarget{ref-light1984}{}}%
Light, Richard J., and David B. Pillemer. 1984. \emph{Summing up; the Science of Reviewing Research}. Cambridge, MA (USA) Harvard Univ. Press.

\leavevmode\vadjust pre{\hypertarget{ref-lisker1977rapid}{}}%
Lisker, Leigh. 1977. {``Rapid Versus Rabid: A Catalogue of Acoustic Features That May Cue the Distinction.''} \emph{The Journal of the Acoustical Society of America} 62 (S1): S77--78.

\leavevmode\vadjust pre{\hypertarget{ref-lisker1986voicing}{}}%
---------. 1986. {``{`Voicing'} in {E}nglish: A Catalogue of Acoustic Features Signaling /b/ Versus /p/ in Trochees.''} \emph{Language and Speech} 29 (1): 3--11.

\leavevmode\vadjust pre{\hypertarget{ref-miguel2014promoting}{}}%
Miguel, Edward, Colin Camerer, Katherine Casey, Joshua Cohen, Kevin M Esterling, Alan Gerber, Rachel Glennerster, et al. 2014. {``Promoting Transparency in Social Science Research.''} \emph{Science} 343 (6166): 30--31.

\leavevmode\vadjust pre{\hypertarget{ref-nickerson1998confirmation}{}}%
Nickerson, Raymond S. 1998. {``Confirmation Bias: A Ubiquitous Phenomenon in Many Guises.''} \emph{Review of General Psychology} 2 (2): 175--220.

\leavevmode\vadjust pre{\hypertarget{ref-nosek2014method}{}}%
Nosek, Brian A, and Daniël Lakens. 2014. {``A Method to Increase the Credibility of Published Results.''} \emph{Social Psychology} 45 (3): 137--41.

\leavevmode\vadjust pre{\hypertarget{ref-ogden2004}{}}%
Ogden, Richard. 2004. {``Non-Modal Voice Quality and Turn-Taking in {F}innish.''} \emph{Sound Patterns in Interaction: Cross-Linguistic Studies from Conversation}, 29--62.

\leavevmode\vadjust pre{\hypertarget{ref-paraboni2007generating}{}}%
Paraboni, Ivandré, Kees Van Deemter, and Judith Masthoff. 2007. {``Generating Referring Expressions: Making Referents Easy to Identify.''} \emph{Computational Linguistics} 33 (2): 229--54.
